Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
Wording

To test properties, we also use GHCi.  Each property is enclosed
within ``\verb|quickCheck (|'' and ``\verb|)|'' string and GHCi
evaluates it.  Success or failures is decided according to result
string from GHCi.

If properties contain free variables, we need to add lambda
abstraction prefix before prepending the `quickCheck'' string.  To
check if properties contain free variables, we also use GHCi for easy
implementation at this moment.  GHCi reports free variables if found:

>>>>

To test properties, we use GHCi.  Each property is enclosed within
``\verb|quickCheck (|'' and ``\verb|)|'', and GHCi is used to evaluate
that.  GHCi output is used to decide, whether the property succeeded,
or failed.

If a property contains free variables, we need to add lambda
abstraction prefix before prepending the `quickCheck'' string.  To
check if properties contain free variables, we also use GHCi for easy
implementation at this moment.  GHCi reports free variables if found:
